Radio Emission from Red-Giant Hot Jupiters

### 2015-09-22 ms.tex
changed the order of appendix

In principle, if the expected luminosity function (LF) and positional distribution of possible RGHJ emitters were known, one could estimate the likelihood of detecting RGHJs in radio surveys. 
For illustration we consider a hypothetical power-law distribution for the RGHJ luminosity function $N[L] \propto L^{-\alpha_L}$, where, $N[L]$ is the number of objects per unit volume with a luminosity of $L$, and assume an isotropic distribution of sources in the observed volume. 
Under these assumptions, the largest luminosity in a volume limited sample (volume $V$) would be such that $V n[L] = 1$, i.e., $L \propto d^{3/\alpha _L}$. The flux of such target at distance $d$ is $F \propto d^{\frac{3}{\alpha_L} - 2}$. 
Therefore,the likelihood of finding the brighter source increases with distance for $\alpha_L < 3/2$. 
Such a scenario would indeed be favorable to detect RGHJs given that RGs and AGB stars with high mass loss rates are rare and would require probing out to larger distances for detection. 
For example, for an $N(L) \propto L^{-1}$ the brightest source within a given distance will increase linearly with distance, making it favorable for detecting intrinsically rare objects. 
Therefore, it is important to determine the LF for RGHJ emitters in order to estimate their detectability.

Planning future targeted surveys of RGHJs would require accurate distribution functions of various parameters of giant stars in the local galaxy. 
In order to estimate the true luminosity function of RGHJ emitters one of the key factors is the distribution of mass-loss rates of giant host stars. 
As discussed in Section~3.2, for a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
Employing equation (\ref{eq:mass-loss}) which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{2/3} R_\star ^{-1/6} M_\star^{1/6} T_{\rm eff}^{2.3} (1+A/g_\star)^{2/3}$. 
Given that the dependences on $R_\star$ and $M_\star^{1/6}$ are relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity due to planets are roughly $L \propto L_{\star }^{2/3}$. 
Thus,  the criteria $\alpha _L < 3/2$ is satisfied if the slope of the luminosity function of the stars are not steeper than $-1$.

@@

In summary, we write down the scaling of the radio emission as below, 
%%%
\begin{equation}
P_{\rm rad} \times 10^{11} \,{\rm W}\, \left( \frac{\omega}{\omega _J} \right)^{\alpha } \left( \frac{M_p}{M_J} \right)^{\beta }  \left( \frac{t}{4.5 \rm~Gyr} \right)^{-\gamma }  \left( \frac{a}{a_J} \right)^{-\delta }  \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{\epsilon } \left( \frac{v}{v_{\odot}} \right)^{\phi } \, \\
\end{equation} 
%%%
with $\alpha = 0.5-0.8$, $\beta = 0.33-1.33$, $\gamma = 0-0.288$, $\gamma = 1.17-1.60$, $\epsilon = 0.58-0.8$, $\phi = 1.46-2.0$.

>>>>

In principle, if the expected luminosity function and positional distribution of possible RGHJ emitters were known, one could estimate the likelihood of detecting RGHJs in radio surveys. 
For illustration we consider a hypothetical power-law distribution for the RGHJ luminosity function $N[L] \propto L^{-\alpha_L}$, where, $N[L]$ is the number of objects per unit volume with a luminosity of $L$, and assume an isotropic distribution of sources in the observed volume. 
Under these assumptions, the largest luminosity in a volume limited sample (volume $V$) would be such that $V n[L] = 1$, i.e., $L \propto d^{3/\alpha _L}$.
The flux of such target at distance $d$ is $F \propto d^{\frac{3}{\alpha_L} - 2}$. 
Therefore,the likelihood of finding the brighter source increases with distance for $\alpha_L < 3/2$. 
Such a scenario would indeed be favorable to detect RGHJs given that RGs and AGB stars with high mass loss rates are rare and would require probing out to larger distances for detection. 
For example, for an $N[L] \propto L^{-1}$ the apparently brightest source within a given distance will increase linearly with distance, making it favorable for detecting intrinsically rare objects. 
Therefore, if we can estimate the luminosity function of RGHJ emitters, we may estimate their detectability.

Planning future targeted surveys of RGHJs would require accurate distribution functions of various parameters of giant stars in our neighborhood of the Galaxy.
In order to estimate the true luminosity function of RGHJ emitters, one of the key factors is the distribution of mass-loss rates of giant host stars. 
As discussed in Section~3.2,\memoDS{Replace ``3.2'' with the section label.} for a given set of orbital parameters the luminosity ($L$) of a RGHJ depends on the stellar mass-loss rate and wind velocity as $\dot{M}_\star^{2/3} v^{5/3}$. 
Employing equation (\ref{eq:mass-loss}) which implies $\dot{M}_\star \propto L_\star^{7.5/4} R_\star^{-0.75} M_\star^{-1} (1+A/g_\star)$ and crudely estimating the wind velocity as $v \propto \sqrt{GM/R} \propto M^{1/2} R^{-1/2}$, the luminosity of the RGHJ radio emission is given by $L \propto L_\star^{2/3} R_\star ^{-1/6} M_\star^{1/6} T_{\rm eff}^{2.3} (1+A/g_\star)^{2/3}$. 
Given that the dependences on $R_\star$ and $M_\star^{1/6}$ are relatively weak and that $T_{\rm eff}$ does not change significantly, the radio luminosity of RGHJs scales roughly as $L \propto L_{\star }^{2/3}$.
Thus, the criterion $\alpha_L < 3/2$ is satisfied if the slope of the luminosity function of the host stars is shallower than $-1$.

@@

In summary, we write down the scaling of the radio emission as below, 
%%%
\begin{equation}
P_{\rm rad} \times 10^{11} \,{\rm W}\, \left( \frac{\omega}{\omega _J} \right)^{\alpha } \left( \frac{M_p}{M_J} \right)^{\beta }  \left( \frac{t}{4.5 \rm~Gyr} \right)^{-\gamma }  \left( \frac{a}{a_J} \right)^{-\delta }  \left( \frac{\dot M_\star}{\dot M_{\odot}} \right)^{\epsilon } \left( \frac{v}{v_{\odot}} \right)^{\phi } \, \\
\end{equation} 
%%%
with $\alpha = 0.5-0.8$, $\beta = 0.33-1.33$, $\gamma = 0-0.288$, $\gamma = 1.17-1.60$, $\epsilon = 0.58-0.8$, $\phi = 1.46-2.0$. 
\end{document}
